# Leaderboard {#sec-leaderboard}

## Fall 2023

This is the leaderboard for the fall of 2023 Land-Use and Land-Cover competition (complementing the Land-Use and Land-Cover mapping chapter). Submissions are required, but the competition is amicable as rankings will only be considered in the general context of grading. Scoring at the level or better than the base model as demonstrated in the course is however required.

### Available data

Training data is generated through a random subset of 200 pixels for each class in the @fritz_global_2017 land-use and land-cover validation dataset (following the chapter's example but with additional data products provided). The equivalent test data for this competition consists of 600 unlabelled locations providing the same spectral information as provided in the training data. Data for the competition can be downloaded from [a dedicated zenodo archive](https://zenodo.org/record/8298491).

### Leaderboard submission

Your model should be able to run on the test dataset, which puts constraints on which additional data you could download. Submit your model results run on the test dataset as a CSV file containing a table of model results (one label on each row, and a header called `lulc_class`).

```{r echo = FALSE}
library(kableExtra)
# demo data
demo <- data.frame(
  lulc_class = c(1,3,5, "...")
)

# plot the matrix as a leaderboard table
kbl(demo) |>
  kable_styling(
    full_width = FALSE
  )
```

Leaderboard submissions will be accepted two (2) times during the semester, with a final submission included with your overall report. The CSV file submitted **via pull request** to [this repo](https://github.com/geco-bern/agds2_course) should be named `xyz_results.csv` (with xyz replaced by your github handle), and put int the `data/leaderboard/fall_2023/` folder. Submissions via email will not be considered.

## Leaderboard

```{r echo=TRUE, message = FALSE, warning = FALSE, error = FALSE, include = FALSE}
library(stringr)

# check if on github
ON_GIT <- ifelse(
  Sys.getenv("GITHUB_ACTION") == "",
  FALSE,
  TRUE
)

# if not on git generate demo files
if(!ON_GIT) {
 
  # generate local random reference set
  reference <- data.frame(
    lulc_class = sample(1:10, 100, replace = TRUE)
  )
    
  # write.table(
  #   reference,
  #   here::here("data/leaderboard/fall_2023/random_results.csv"),
  #   col.names = TRUE,
  #   row.names = FALSE, 
  #   quote = FALSE
  # )
} else {
  reference <- Sys.getenv("LULC")
  
  # convert from dirty string
  # to numeric (check these break
  # now every line is a value in the environmental
  # variable defined in github settings when a long
  # string this would be a space or tab)
  reference <- as.numeric(unlist(strsplit(reference, "\r\n")))
  
  # reshuffle into data frame
  reference <- data.frame(
    lulc_class = reference
  )
}

# list csv file in data/leaderboard/fall_2023
files <- list.files(
  here::here("data/leaderboard/fall_2023"),
  "*.csv",
  full.names = TRUE
  )

# loop over all files
lb <- lapply(files, function(file){
  
  # read in leaderboard submission
  modelled <- read.table(file, header = TRUE, sep = ",")
  
  # calculate confusion matrix
  cm <-  try(
    caret::confusionMatrix(
      data = as.factor(modelled$lulc_class),
      reference = as.factor(reference$lulc_class)
    )
  )
  
  # trap confusion matrix errors (if any)
  if(inherits(cm, "try-error")){
    return(NULL)
  } else {
    # split out overall accuracy and kappa
    cm <- round(cm$overall[1:2], 4)
    
    # set users
    user <- gsub("_results.csv", "", basename(file))
    
    # bind to results
    cm <- data.frame(
      User = user,
      Accuracy = cm[1],
      Kappa = cm[2],
      row.names = NULL
    )
    
    return(cm)
  }
})

# bind rows
lb <- do.call("rbind", lb)
```

```{r echo=FALSE, message = FALSE, warning = FALSE, error = FALSE}
if(!is.null(lb)) {
  # order rows from high to low
  lb <- lb[order(lb$Accuracy, decreasing = TRUE),]
  
  # plot the matrix as a leaderboard table
  kbl(
    lb,
    caption = "The leaderboard ranked according to highest accuracy score. A random dataset is included as a reference, as well as the default model as demonstrated in the Handful of Pixels LULC chapter."
  ) |>
    kable_styling(
      bootstrap_options = "striped",
      full_width = TRUE
    ) |>
    footnote(
      ifelse(ON_GIT,
             "This table was automatically generated! Updates after submission can take over 10 minutes.",
             "This is a dummy local render for debugging purposes."
             )
    )
}
```

